MADA Project - Ibis Blood Parasites from Florida

### 2021-10-18 products/manuscript/Manuscript.Rmd
Altered Structure of Project Repo 10/18/21
Completely changed the structure of the overall project repo. Manuscript still needs altering to accommodate the changes.

```{r}
#Setting the path to the Ibis blood parasite spreadsheet
data_locationIbisB <- here::here("data","raw_data","Ibis_Blood_ParasiteData_2017.xlsx")

@@

```{r}
#Setting the path to the Ibis field data spreadsheet
data_locationIbisF <- here::here("data","raw_data","IbisFieldDataOct19_2017.xlsx")

@@

```{r}
#Setting the path to the first Ibis supplemental excel sheet (Urban Gradients)
data_locationIbisUr <- here::here("data","raw_data","100IbisID_UrbanGradient.xlsx")

@@

```{r}
#Setting the path to the second Ibis supplemental excel sheet (Salmonella)
data_locationIbisSal <- here::here("data","raw_data","SalmonellaFieldSerotypesAug27_2018.xlsx")

@@

#Saving the Ibis Blood 10-14 dataset as an RDS in the processed data folder
save_data_location <- here::here("data", "processed_data", "processedIbisBlood10_14.rds")
saveRDS(IbisBlood10_14, file = save_data_location)

#Saving the Ibis Blood 15-17 dataset as an RDS in the processed data folder
save_data_location2 <- here::here("data", "processed_data", "processedIbisBlood15_17.rds")
saveRDS(IbisBlood15_17, file = save_data_location2)

>>>>

```{r}
#Setting the path to the Ibis blood parasite spreadsheet
data_locationIbisB <- here::here("raw_data","Ibis_Blood_ParasiteData_2017.xlsx")

@@

```{r}
#Setting the path to the Ibis field data spreadsheet
data_locationIbisF <- here::here("raw_data","IbisFieldDataOct19_2017.xlsx")

@@

```{r}
#Setting the path to the first Ibis supplemental excel sheet (Urban Gradients)
data_locationIbisUr <- here::here("raw_data","100IbisID_UrbanGradient.xlsx")

@@

```{r}
#Setting the path to the second Ibis supplemental excel sheet (Salmonella)
data_locationIbisSal <- here::here("raw_data","SalmonellaFieldSerotypesAug27_2018.xlsx")

@@

#Saving the Ibis Blood 10-14 dataset as an RDS in the processed data folder
save_data_location <- here::here("processed_data", "processedIbisBlood10_14.rds")
saveRDS(IbisBlood10_14, file = save_data_location)

#Saving the Ibis Blood 15-17 dataset as an RDS in the processed data folder
save_data_location2 <- here::here("processed_data", "processedIbisBlood15_17.rds")
saveRDS(IbisBlood15_17, file = save_data_location2)
